---
title: "Building up the match accuracy model"
output:
  html_document:
    theme: flatly
---

```{r, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

library(tidyverse)
library(magrittr)
library(lme4)
library(AICcmodavg)

# devtools::install_github("lupyanlab/words-in-transition", subdir = "wordsintransition")
library(wordsintransition)


# Load the results of the "Guess the seed" surveys.
data("imitation_matches")
imitation_matches %<>%
  filter(question_type != "catch_trial") %>%  # Drop catch trials
  recode_generation() %>%                     # Create generation_1 variable
  recode_survey_type() %>%                    # Create treatment contrasts
  add_chance()                                # Add column for chance offset


# Theme colors
colors <- RColorBrewer::brewer.pal(4, "Set2")
names(colors) <- c("blue", "orange", "green", "pink")
question_type_levels <- recode_survey_type()$survey_type
question_type_labels <- c("True seed", "Category match", "Specific match")
question_type_colors <- unname(colors[c("blue", "green", "orange")])

# Create a base plot without any layers, just setting up
# the axes and theme.
base_plot <- ggplot(imitation_matches) +
  aes(x = generation_1, y = is_correct, color = survey_type) +
  scale_x_continuous("Generation", breaks = 0:7, labels = 1:8) +
  scale_y_continuous("Accuracy", breaks = seq(0, 1, by = 0.1),
                     labels = scales::percent) +
  scale_color_manual("", labels = question_type_labels, values = question_type_colors) +
  geom_hline(yintercept = 0.25, lty = 2, alpha = 0.4, size = 1) +
  coord_cartesian(xlim = c(-0.2, 7.2)) +
  theme_minimal() +
  theme(
    legend.position = c(0.8, 0.85),
    legend.key.width = unit(5, "lines"),
    panel.grid.minor.x = element_blank()
  )
```

# Means grouped by seed

The seed is the primary unit of analysis. Each seed is used in approximately 4 different transmission chains. We are collapsing across all of the chains leading from each seed for this analysis.

```{r, echo=FALSE, fig.width=2, results="hide"}
library(crotchet)  # devtools::install_github("pedmiston/crotchet")
draw_graphviz("definitions", "wordsintransition")
```

Since each imitation is tested in three different survey conditions, the following plot has a total of 48 lines (16 seeds x 3 lines for each seed).

```{r}
# Show means grouped by seed. Each seed is used
# in approximately 4 transmission chains.
create_question_type_by_seed_id <- . %>% 
  mutate(question_type_by_seed_id = paste(survey_type, seed_id, sep = ":"))

imitation_matches %<>% create_question_type_by_seed_id()
base_plot <- base_plot %+% imitation_matches

seed_means <- imitation_matches %>%
  group_by(seed_id, survey_type, generation) %>%
  summarize(
    is_correct = mean(is_correct),
    n = n()
  ) %>%
  ungroup() %>%
  create_question_type_by_seed_id() %>%
  recode_generation()

# Show means with lines connecting the raw means at each generation
base_plot +
  geom_line(aes(group = question_type_by_seed_id, color = survey_type),
            data = seed_means) +
  geom_point(aes(size = n, color = survey_type),
             data = seed_means) +
  scale_size_continuous("Num survey responses") +
  theme(legend.position = "right")
```

# Fit loess lines

These loess lines are fit to the raw data, so they reflect the different number of observations at each generation.

```{r}
base_plot +
  geom_smooth(aes(group = question_type_by_seed_id, color = survey_type),
              method = "loess", se = FALSE) +
  geom_point(aes(size = n, color = survey_type),
             data = seed_means) +
  scale_size_continuous("Num survey responses") +
  theme(legend.position = "right")
```

# Fit lm lines

```{r}
base_plot +
  geom_smooth(aes(group = question_type_by_seed_id, color = survey_type),
              method = "lm", data = seed_means, se = FALSE) +
  geom_point(aes(size = n, color = survey_type),
             data = seed_means) +
  scale_size_continuous("Num survey responses") +
  theme(legend.position = "right")
```

Note that there are very few positively sloped lines. This indicates that any uptick in matching accuracy at the end of the chains (near generation == 8) is misleading.

# Show facet plots for each seed

Here is the most accurate plot that represents the model we are fitting. There are 16 facets, one for each seed, and for each seed, we are fitting 3 lines, one for each question type.

```{r, fig.width=10, fig.height=10}
seed_map <- imitation_matches %>%
  select(seed_id, category = chain_name) %>%
  unique() %>%
  group_by(category) %>%
  arrange(seed_id) %>%
  mutate(seed_ix = 1:n()) %>%
  ungroup()
imitation_matches %<>% left_join(seed_map)
seed_means %<>% left_join(seed_map)
base_plot <- base_plot %+% imitation_matches

base_plot +
  geom_smooth(aes(group = question_type_by_seed_id, color = survey_type),
              method = "lm", data = seed_means, se = FALSE) +
  geom_point(aes(size = n, color = survey_type),
             data = seed_means, alpha = 0.6) +
  scale_size_continuous("Num survey responses") +
  theme(legend.position = "right") +
  facet_grid(category ~ seed_ix)
```

# Fit the hierarchical model

This model estimates what is true about the relationship between the three lines within each of the facets in the plot immediately above this one.

```{r cache=TRUE}
imitation_matches_mod <- glmer(
  is_correct ~ offset(chance_log) + generation_1 * (same_v_between + same_v_within) +
    (generation_1|chain_name/seed_id) + (1|subj_id),
  family = "binomial", data = imitation_matches
)
```

```{r}
imitation_matches_preds <- expand.grid(
    generation_1 = unique(imitation_matches$generation_1) %>% na.omit(),
    survey_type = c("between", "same", "within"),
    stringsAsFactors = FALSE
  ) %>%
  recode_survey_type() %>%
  recode_generation() %>%
  add_chance() %>%
  cbind(., predictSE(imitation_matches_mod, newdata = ., se = TRUE)) %>%
  rename(is_correct = fit, se = se.fit)

base_plot +
  geom_point(aes(size = n, color = survey_type),
             data = seed_means, alpha = 0.6,
             position = position_jitter(width = 0.2)) +
  scale_size_continuous("Num survey responses") +
  theme(legend.position = "right") +
  geom_smooth(aes(color = survey_type, ymin = is_correct - se, ymax = is_correct + se),
              stat = "identity", data = imitation_matches_preds)
```

# Transform the means for each seed by subtracting out random effects

```{r}
library(broom)
library(stringr)

# Get random effects as a list with different grouping variables as keys
imitation_matches_ranefs <- ranef(imitation_matches_mod)

# Process the chain_name effects
# A better name for chain_name would be category
category_effects <- imitation_matches_ranefs$chain_name %>%
  as.data.frame() %>%
  rename(
    category_intercept = `(Intercept)`,
    category_slope = generation_1
  ) %>%
  do({ mutate(., category = rownames(.)) })

# Process the seed effects
# The grouping variable is seed_id:chain_name
seed_effects <- imitation_matches_ranefs$`seed_id:chain_name` %>%
  as.data.frame() %>%
  rename(
    seed_intercept = `(Intercept)`,
    seed_slope = generation_1
  )

# Extract the seed_id and chain_name values from the grouping variable
seed_effects[c("seed_id", "category")] <- str_split_fixed(rownames(seed_effects), ":", 2) %>%
  as_data_frame() %>%
  mutate(V1 = as.numeric(V1))

# Merge the two levels of random effect vars
seed_category_ranefs <- left_join(category_effects, seed_effects)

# Get predictions for each generation
seed_category_preds <- expand.grid(
    seed_id = seed_category_ranefs$seed_id,
    generation_1 = 0:7
  ) %>%
  left_join(seed_category_ranefs) %>%
  mutate(
    offset = (seed_intercept + seed_slope * generation_1) + 
             (category_intercept + category_slope * generation_1)
  ) %>%
  select(seed_id, generation_1, offset)

# Extract the random effects from the means
seed_means %<>%
  left_join(seed_category_preds) %>%
  mutate(is_correct_adj = is_correct + offset)

base_plot +
  geom_point(aes(y = is_correct_adj, size = n, color = survey_type),
             data = seed_means, alpha = 0.6,
             position = position_jitter(width = 0.2)) +
  scale_size_continuous("Num survey responses") +
  theme(legend.position = "right") +
  geom_smooth(aes(color = survey_type, ymin = is_correct - se, ymax = is_correct + se),
              stat = "identity", data = imitation_matches_preds)
```