---
title: "Design"
author: "Pierce Edmiston"
output:
  html_document:
    theme: flatly
    toc: true
---

```{r config, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  fig.path = "figs/",
  cache = TRUE,
  cache.path = ".cache/"
)
```

# Sounds

```{r telephone-game, engine = "dot"}
digraph {
  node[fontname="helvetica", fontsize=30];

  glass -> {glass1, glass2, glass3, glass4};
  tear -> {tear1, tear2, tear3, tear4};
  water -> {water1, water2, water3, water4};
  zipper -> {zipper1, zipper2, zipper3, zipper4};
  
  glass[shape="none"];
  tear[shape="none"];
  water[shape="none"];
  zipper[shape="none"];

  glass1[label="seed 1"];
  glass2[label="2"];
  glass3[label="3"];
  glass4[label="4"];

  tear1[label="1"];
  tear2[label="2"];
  tear3[label="3"];
  tear4[label="4"];

  water1[label="1"];
  water2[label="2"];
  water3[label="3"];
  water4[label="4"];

  zipper1[label="1"];
  zipper2[label="2"];
  zipper3[label="3"];
  zipper4[label="4"];

  glass1 -> {subj1, subj2, subj3, subj4};

  subj1[label="branch 1\ngen 1"];
  subj2[label="2"];
  subj3[label="3"];
  subj4[label="4"];
  
  gen2[label="2"];
  gen3[label="3"];
  gen4[label="4"];
  gen5[label="5"];
  gen6[label="6"];
  gen7[label="7"];
  gen8[label="branch 1\ngen 8"];
  
  subj1 -> gen2 -> gen3 -> gen4 -> gen5 -> gen6 -> gen7 -> gen8;
  
}
```

# Imitation matches

Each imitation is matched in three different "guess the seed" conditions:

1. Category match (true seed)
2. Category match
3. Specific match

```{r category-match-true-seed, engine = "dot"}
digraph {
  labelloc="t";
  label="Category match (true seed)";

  graph[fontname="helvetica", fontsize=30];
  node[fontname="helvetica", fontsize=30];
  
  glass[shape="none"];
  tear[shape="none"];
  water[shape="none"];
  zipper[shape="none"];

  glass -> {glass1, glass2, glass3, glass4};
  tear -> {tear1, tear2, tear3, tear4};
  water -> {water1, water2, water3, water4};
  zipper -> {zipper1, zipper2, zipper3, zipper4};

  glass1[style="filled", fillcolor="#66C2A5"];
  tear2[style="filled", fillcolor="#66C2A5"];
  water3[style="filled", fillcolor="#66C2A5"];
  zipper4[style="filled", fillcolor="#66C2A5"];

  glass1[label="1"];
  glass2[label="2"];
  glass3[label="3"];
  glass4[label="4"];

  tear1[label="1"];
  tear2[label="2"];
  tear3[label="3"];
  tear4[label="4"];

  water1[label="1"];
  water2[label="2"];
  water3[label="3"];
  water4[label="4"];

  zipper1[label="1"];
  zipper2[label="2"];
  zipper3[label="3"];
  zipper4[label="4"];

  tear2 -> gen1;
  gen1[label="?", style="filled", fillcolor="#FC8D62"];
}
```

```{r category-match, engine = "dot"}
digraph {
  labelloc="t";
  label="Category match";

  graph[fontname="helvetica", fontsize=30];
  node[fontname="helvetica", fontsize=30];
  
  glass[shape="none"];
  tear[shape="none"];
  water[shape="none"];
  zipper[shape="none"];

  glass -> {glass1, glass2, glass3, glass4};
  tear -> {tear1, tear2, tear3, tear4};
  water -> {water1, water2, water3, water4};
  zipper -> {zipper1, zipper2, zipper3, zipper4};

  glass1[style="filled", fillcolor="#66C2A5"];
  tear3[style="filled", fillcolor="#66C2A5"];
  water3[style="filled", fillcolor="#66C2A5"];
  zipper4[style="filled", fillcolor="#66C2A5"];

  glass1[label="1"];
  glass2[label="2"];
  glass3[label="3"];
  glass4[label="4"];

  tear1[label="1"];
  tear2[label="2"];
  tear3[label="3"];
  tear4[label="4"];

  water1[label="1"];
  water2[label="2"];
  water3[label="3"];
  water4[label="4"];

  zipper1[label="1"];
  zipper2[label="2"];
  zipper3[label="3"];
  zipper4[label="4"];

  tear2 -> gen1;
  gen1[label="?", style="filled", fillcolor="#FC8D62"];
}
```

```{r specific-match, engine = "dot"}
digraph {
  labelloc="t";
  label="Specific match";

  graph[fontname="helvetica", fontsize=30];
  node[fontname="helvetica", fontsize=30];
  
  glass[shape="none"];
  tear[shape="none"];
  water[shape="none"];
  zipper[shape="none"];

  glass -> {glass1, glass2, glass3, glass4};
  tear -> {tear1, tear2, tear3, tear4};
  water -> {water1, water2, water3, water4};
  zipper -> {zipper1, zipper2, zipper3, zipper4};

  tear1[style="filled", fillcolor="#66C2A5"];
  tear2[style="filled", fillcolor="#66C2A5"];
  tear3[style="filled", fillcolor="#66C2A5"];
  tear4[style="filled", fillcolor="#66C2A5"];

  glass1[label="1"];
  glass2[label="2"];
  glass3[label="3"];
  glass4[label="4"];

  tear1[label="1"];
  tear2[label="2"];
  tear3[label="3"];
  tear4[label="4"];

  water1[label="1"];
  water2[label="2"];
  water3[label="3"];
  water4[label="4"];

  zipper1[label="1"];
  zipper2[label="2"];
  zipper3[label="3"];
  zipper4[label="4"];

  tear2 -> gen1;
  gen1[label="?", style="filled", fillcolor="#FC8D62"];
}
```

# Transcriptions

Each imitation is transcribed by 10-20 different people. The unique transcriptions are rated in two match to seed surveys.

Each imitation can be summarized:

1. Transcription agreement
2. Average "guess the seed" accuracy for top X transcriptions

Each transcription can be summarized:

1. Category match (true seed)
2. Category match

```{r transcriptions, engine = "dot"}
digraph {
  node[fontname="helvetica", fontsize=30];
  edge[splines=line];

  imitation -> {a, b, c, d, e, f, g, h, i, j};
  
  imitation[label="Imitation X", shape=none];

  a[label="Transcription 1"];
  b[label="2"];
  c[label="3"];
  d[label="4"];
  e[label="5"];
  f[label="6"];
  g[label="7"];
  h[label="8"];
  i[label="9"];
  j[label="10"];
  
  a -> {category_match_true_seed, category_match};
  
  category_match_true_seed[label="Category match\n(true seed)", shape=none];
  category_match[label="Category match", shape=none];
}
```