---
title: "The emergence of lexical categories from iterated vocal imitation"
author: "Pierce Edmiston"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
---

```{r config, echo = FALSE}
library(knitr)
library(printr)

opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  cache.path = ".cache/",
  fig.path = "figs/",
  fig.width = 8
)

read_chunk("theme.R")

# read_chunk("1-determine-seeds/results.R")
# read_chunk("2-collect-imitations/results.R")
read_chunk("3-match-to-seed-imitations/results.R")
read_chunk("4-collect-transcriptions/results.R")
read_chunk("5-transcription-matches/results.R")
```

```{r setup}
library(dplyr)
library(magrittr)
library(stringr)
library(ggplot2)
library(scales)
library(lme4)
library(broom)
library(AICcmodavg)

library(wordsintransition)
data("imitation_matches")
data("transcription_matches")

transcription_matches %<>%
  recode_question_type %>%
  recode_message_type %>%
  recode_version
```

```{r global-theme}
```

# Seed selection

We started with 6 sounds in each of 6 categories and reduced that number to 4 sounds in each of 4 categories through two "odd one out" norming experiments.

# Collecting imitations

## Methods

```{r telephone-game, engine = "dot"}
digraph {
  node[fontname="helvetica", fontsize=30];

  glass -> {glass1, glass2, glass3, glass4};
  tear -> {tear1, tear2, tear3, tear4};
  water -> {water1, water2, water3, water4};
  zipper -> {zipper1, zipper2, zipper3, zipper4};
  
  glass[shape="none"];
  tear[shape="none"];
  water[shape="none"];
  zipper[shape="none"];

  glass1[label="seed 1"];
  glass2[label="2"];
  glass3[label="3"];
  glass4[label="4"];

  tear1[label="1"];
  tear2[label="2"];
  tear3[label="3"];
  tear4[label="4"];

  water1[label="1"];
  water2[label="2"];
  water3[label="3"];
  water4[label="4"];

  zipper1[label="1"];
  zipper2[label="2"];
  zipper3[label="3"];
  zipper4[label="4"];

  glass1 -> {subj1, subj2, subj3, subj4};

  subj1[label="branch 1\ngen 1"];
  subj2[label="2"];
  subj3[label="3"];
  subj4[label="4"];
  
  gen2[label="2"];
  gen3[label="3"];
  gen4[label="4"];
  gen5[label="5"];
  gen6[label="6"];
  gen7[label="7"];
  gen8[label="branch 1\ngen 8"];
  
  subj1 -> gen2 -> gen3 -> gen4 -> gen5 -> gen6 -> gen7 -> gen8;
  
}
```

## Results

TODO: Analyze the fidelity of the imitations.

1. From generation to generation
2. Across different branches in the same generation

# Matching imitations to seeds

## Methods

### Question types

Each imitation is matched in three different "guess the seed" conditions:

1. Category match (true seed)
2. Category match
3. Specific match

```{r category-match-true-seed, engine = "dot"}
digraph {
  labelloc="t";
  label="Category match (true seed)";

  graph[fontname="helvetica", fontsize=30];
  node[fontname="helvetica", fontsize=30];
  
  glass[shape="none"];
  tear[shape="none"];
  water[shape="none"];
  zipper[shape="none"];

  glass -> {glass1, glass2, glass3, glass4};
  tear -> {tear1, tear2, tear3, tear4};
  water -> {water1, water2, water3, water4};
  zipper -> {zipper1, zipper2, zipper3, zipper4};

  glass1[style="filled", fillcolor="#66C2A5"];
  tear2[style="filled", fillcolor="#66C2A5"];
  water3[style="filled", fillcolor="#66C2A5"];
  zipper4[style="filled", fillcolor="#66C2A5"];

  glass1[label="1"];
  glass2[label="2"];
  glass3[label="3"];
  glass4[label="4"];

  tear1[label="1"];
  tear2[label="2"];
  tear3[label="3"];
  tear4[label="4"];

  water1[label="1"];
  water2[label="2"];
  water3[label="3"];
  water4[label="4"];

  zipper1[label="1"];
  zipper2[label="2"];
  zipper3[label="3"];
  zipper4[label="4"];

  tear2 -> gen1;
  gen1[label="?", style="filled", fillcolor="#FC8D62"];
}
```

```{r category-match, engine = "dot"}
digraph {
  labelloc="t";
  label="Category match";

  graph[fontname="helvetica", fontsize=30];
  node[fontname="helvetica", fontsize=30];
  
  glass[shape="none"];
  tear[shape="none"];
  water[shape="none"];
  zipper[shape="none"];

  glass -> {glass1, glass2, glass3, glass4};
  tear -> {tear1, tear2, tear3, tear4};
  water -> {water1, water2, water3, water4};
  zipper -> {zipper1, zipper2, zipper3, zipper4};

  glass1[style="filled", fillcolor="#66C2A5"];
  tear3[style="filled", fillcolor="#66C2A5"];
  water3[style="filled", fillcolor="#66C2A5"];
  zipper4[style="filled", fillcolor="#66C2A5"];

  glass1[label="1"];
  glass2[label="2"];
  glass3[label="3"];
  glass4[label="4"];

  tear1[label="1"];
  tear2[label="2"];
  tear3[label="3"];
  tear4[label="4"];

  water1[label="1"];
  water2[label="2"];
  water3[label="3"];
  water4[label="4"];

  zipper1[label="1"];
  zipper2[label="2"];
  zipper3[label="3"];
  zipper4[label="4"];

  tear2 -> gen1;
  gen1[label="?", style="filled", fillcolor="#FC8D62"];
}
```

```{r specific-match, engine = "dot"}
digraph {
  labelloc="t";
  label="Specific match";

  graph[fontname="helvetica", fontsize=30];
  node[fontname="helvetica", fontsize=30];
  
  glass[shape="none"];
  tear[shape="none"];
  water[shape="none"];
  zipper[shape="none"];

  glass -> {glass1, glass2, glass3, glass4};
  tear -> {tear1, tear2, tear3, tear4};
  water -> {water1, water2, water3, water4};
  zipper -> {zipper1, zipper2, zipper3, zipper4};

  tear1[style="filled", fillcolor="#66C2A5"];
  tear2[style="filled", fillcolor="#66C2A5"];
  tear3[style="filled", fillcolor="#66C2A5"];
  tear4[style="filled", fillcolor="#66C2A5"];

  glass1[label="1"];
  glass2[label="2"];
  glass3[label="3"];
  glass4[label="4"];

  tear1[label="1"];
  tear2[label="2"];
  tear3[label="3"];
  tear4[label="4"];

  water1[label="1"];
  water2[label="2"];
  water3[label="3"];
  water4[label="4"];

  zipper1[label="1"];
  zipper2[label="2"];
  zipper3[label="3"];
  zipper4[label="4"];

  tear2 -> gen1;
  gen1[label="?", style="filled", fillcolor="#FC8D62"];
}
```

### Number of responses per question

```{r 3-setup}
```

```{r 3-data}
```

```{r 3-num-responses-per-question}
```

## Results

```{r 3-models}
```

```{r 3-first-gen}
```

```{r 3-match-to-seed}
```

```{r 3-first-last-gen}
```

# Transcriptions of imitations

```{r 4-setup}
```

## Methods

### Selected sounds

Transcribed sounds include all 16 seed sound effects and all imitatations in the last generation of each iteration chain.

```{r 4-num-sounds-transcribed}
```

### Number of transcriptions for each sound

```{r 4-num-transcriptions-per-imitation, fig.width = 14}
```

## Results

### Exact agreement

Transcription agreement for each sound, controlling for case only. Messages with no agreement among transcriptions had all unique transcriptions.

There was less agreement among transcribers for the seed sound effects
than there was among the transcribers of n-th generation imitations.

```{r 4-transcription-agreement-exact}
```

### Pattern distance

Transcription agreement by average pattern match distance to the single most frequent transcription. For messages with no duplicate transcriptions, distances are calculated relative to a randomly selected transcription (and therefore the distance metric is inappropriate).

```{r 4-transcription-agreement-distance}
```

### Length of pattern

```{r 4-transcription-length}
```

### Phonological similarity

TODO: Confusability matrix

# Matching transcriptions to seeds

```{r 5-setup}
```

## Methods

### Selected transcriptions

We obtained match-to-seed accuracy ratings for the 4 most frequent spellings
of a sample of 8 transcribed sounds.

### Subjects

```{r, 5-subjects}
transcription_matches %>%
  group_by(version) %>%
  summarize(
    num_subjects = length(unique(subj_id)),
    num_responses_per_subject = round(n()/num_subjects)
  ) %>%
  kable(col.names = c("Version", "Subjects", "Responses per subject"),
        align = "l")
```

Subjects were excluded if they failed the catch trial, which indicated
that they should select the third option.

```{r 5-catch-trials, fig.width = 4}
```

### Number of responses

```{r 5-responses-per-question}
```

## Results

```{r 5-plot-template}
```

```{r 5-plot-means}
```

```{r 5-model, echo = 1, cache = TRUE}
```

```{r 5-model-preds}
```

### Agreement as a predictor of matching accuracy

Do the imitations where there is a lot of agreement in the transcriptions have higher matching accuracy?

```{r 5-transcription-agreement-matching-accuracy}
```