---
title: "The emergence of lexical categories from iterated vocal imitation"
author: "Pierce Edmiston, Marcus Perlman, and Gary Lupyan"
output:
  html_document:
    theme: flatly
---

This research intends to show that conventionalized word forms can arise gradually and uneffortfully simply through the repeated imitation of nonverbal, environmental sounds. Participants played an online version of the children's game "telephone" where an auditory message is passed from person to person with the goal of keeping the message unchanged. Instead of a typical message, participants had to pass on imitations of nonverbal environment sounds (e.g., glass breaking, water splashing). These imitations were hypothesized to become more wordlike as they are repeated.

```{r config, echo = FALSE, warning = FALSE, message = FALSE, results = "hide"}
library(knitr)
library(printr)
library(broom)
library(DiagrammeR)
library(grid)
library(gridExtra)
library(png)
library(dplyr)
library(crotchet)  # devtools::install_github("pedmiston/crotchet")

opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = "hide",
  cache = TRUE,
  cache.path = ".cache/",
  fig.path = "figs/",
  fig.width = 10,
  fig.height = 3.5
)

read_chunk("theme.R")

read_results_chunks <- function(experiments) {
  scripts <- paste(experiments, "results.R", sep = "/")
  sapply(scripts, read_chunk)
}

read_results_chunks(c(
  "2-collect-imitations",
  "3-imitation-matches",
  "4-collect-transcriptions",
  "5-transcription-matches",
  "6-learning-sound-names"
))
```

```{r theme}
```

# Collecting imitations

```{r 2-setup}
```

```{r 2-similarity-judgments-mod}
```

```{r 2-similarity-judgments-plot, fig.show = "hide"}
```

```{r telephone-game}
# Make a two-panel plot:
# (A) telephone game design
# (B) acoustic similarity

grid.arrange(
  read_graphviz("definitions", "wordsintransition"),
  gg_similarity_judgments,
  nrow = 1, widths = c(0.4, 0.6)
)
```

# Matching back to original

```{r 3-setup}
```

```{r 3-data}
```

```{r 3-models}
```

```{r 3-match-to-seed, fig.show = "hide"}
```

```{r guess-the-seed}
question_types_grob <- arrangeGrob(
  read_graphviz("true-seed", "wordsintransition"),
  read_graphviz("category-match", "wordsintransition"),
  read_graphviz("specific-match", "wordsintransition"),
  ncol = 1
)

grid.arrange(
  question_types_grob,
  gg_match_to_seed,
  nrow = 1
)
```

# Transcriptions

```{r 4-setup}
```

```{r 4-transcription-agreement-distance, fig.show = "hide"}
```

```{r 5-setup}
```

```{r 5-match-transcriptions-mod}
```

```{r 5-match-transcriptions-plot, fig.show = "hide"}
```

```{r transcriptions}
grid.arrange(
  gg_distance,
  gg_match_transcriptions,
  nrow = 1
)
```

# Category learning

```{r 6-setup}
```

```{r 6-errors, fig.show = "hide"}
```

```{r 6-rts-over-trials, fig.show = "hide"}
```

```{r 6-results, fig.show = "hide"}
```

```{r category-learning}
grid.arrange(
  (rt_plot %+% first_last_gen) + 
    scale_color_message_label_2 +
    theme(legend.position = "none"),
  (error_plot %+% first_last_gen) +
    theme(legend.position = c(0.8, 0.9)) +
    scale_color_message_label_2,
  nrow = 1
)
```