---
title: "Transcriptions of first and last generation imitations"
author: "Pierce Edmiston"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
---

```{r config, echo = FALSE, message = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.path = "figs/",
  cache = TRUE,
  cache.path = ".cache/"
)

read_chunk("results.R")
```

```{r 4-setup}
```

# Sounds

Sounds comprise sound effects (generation 0) and imitations (generation > 0).

```{r 4-num-sounds}
```

# Transcribed sounds

```{r 4-num-sounds-transcribed}
```

# Transcriptions per sound

```{r 4-num-transcriptions-per-imitation, fig.width = 14}
```

# Transcription agreement

Transcription agreement for each sound, controlling for case only. Messages with no agreement among transcriptions had all unique transcriptions.

```{r 4-transcription-agreement-exact}
```

Transcription agreement by average pattern match distance to the single most frequent transcription. For messages with no duplicate transcriptions, distances are calculated relative to a randomly selected transcription, and therefore the distance metric is inadequate.

```{r 4-transcription-agreement-distance}
```
