---
title: "Transcriptions of first and last generation imitations"
author: "Pierce Edmiston"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
---

```{r config, echo = FALSE, message = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.path = "figs/",
  cache = TRUE,
  cache.path = ".cache/"
)

read_chunk("results.R")

library(ggplot2)
global_theme <- theme_minimal() +
  theme(axis.ticks = element_blank())
```

```{r 4-setup}
```

As imitations were iterated over generations of participants in the telephone game,
the transcriptions of those imitations became more clustered around particular word 
forms. There was more agreement on specific transcriptions at later generations, and 
on average transcriptions become closer together in pattern matching distance.

# Sounds

Sounds comprise sound effects (generation 0) and imitations (generation > 0).

```{r 4-num-sounds}
```

# Transcribed sounds

```{r 4-num-sounds-transcribed}
```

# Transcriptions per sound

```{r 4-num-transcriptions-per-imitation, fig.width = 14}
```

# Transcription agreement

## Exact agreement

Transcription agreement for each sound, controlling for case only. Messages with no agreement among transcriptions had all unique transcriptions.

```{r 4-transcription-agreement-exact}
```

## Pattern distance

Transcription agreement by average pattern match distance to the single most frequent transcription. For messages with no duplicate transcriptions, distances are calculated relative to a randomly selected transcription (and therefore the distance metric is inappropriate).

```{r 4-transcription-agreement-distance}
```

## Length of pattern

```{r 4-transcription-length}
```

