# Collecting imitations

We collected vocal imitations by conducting a version of the children's game
"telephone" online. Starting with the selected seeds, participants imitated either the seed sounds directly or someone's imitation of the seed sound that had been passed down transmission chains of unique participants.

```{r include=FALSE}
library(dplyr)
library(magrittr)
library(ggplot2)
library(lme4)
library(AICcmodavg)

library(wordsintransition)
data("imitations")
data("acoustic_similarity_judgments")
data("subjects")

global_theme <- theme_minimal() +
  theme(
    axis.ticks = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )

z_score_by_subj <- function(frame) {
  z_score <- function(x) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)
  frame %>%
    group_by(name) %>%
    mutate(similarity_z = z_score(similarity)) %>%
    ungroup()
}

recode_edge_generations <- function(frame) {
  data_frame(
    edge_generations = c("1-2", "2-3", "3-4", "4-5", "5-6", "6-7", "7-8"),
    edge_generation_n = seq_along(edge_generations)
  ) %>%
    left_join(frame, .)
}

determine_trial_id <- function(frame) {
  # Warning! Ignores presentation order.
  mutate(frame, trial_id = paste(sound_x, ":", sound_y))
}

acoustic_similarity_judgments %<>%
  mutate(similarity = ifelse(similarity == -1, NA, similarity)) %>%
  z_score_by_subj() %>%
  recode_edge_generations() %>%
  determine_trial_id()
```

## Methods

### Design

```{r 2-definitions, engine="dot", cache=FALSE, code=readLines(crotchet::find_graphviz("definitions", "wordsintransition")), fig.width=2, fig.cap="Design for the telephone game experiment. Imitations were gathered from four categories of sounds and from four seeds within each category. Each seed sound was imitated by four different participants, leading to four different branches off of each seed sound. Branches were allowed to run out for up to 8 generations."}
```

### Participants

Participants were recruited via Amazon's Mechanical Turk. Eligible participants were based in the United States and had a working microphone for recording the imitations.

```{r 2-participants, echo=FALSE, results="asis"}
data_frame(
  Experiment = c("Collect imitations", "Judge similarity"),
  N = c(
    round(nrow(imitations %>% filter(generation > 0))/4, 0),
    length(unique(acoustic_similarity_judgments$name))
  )
) %>%
  pander::pandoc.table()
```

### Procedure

Participants were given a link to the experiment. The experiment was introduced as a version of the children's game "telephone" where an auditory message is passed from person to person with the goal of leaving the original message unchanged. They were told that the messages they would hear might not be recognizable as English words (as they typically are in the children's game), but that their goal was the same: to repeat whatever they heard as accurately as possible. Participants then listened to messages one at a time and recorded their imitation of it for a total of four messages and imitations. The average time to complete this experiment was less than 5 minutes.

```{r, fig.width=3, fig.cap="The interface for the telephone game. Initially the only action open to players is to hear the message by clicking the top sound icon. After listening to the message once, they could then initiate a recording of their imitation by clicking the bottom sound icon. Turning the recorder off submitted their response, and a new message was loaded."}
library(grid)
library(png)
grid.newpage()
grid.draw(readPNG("img/telephone.png") %>% rasterGrob())
```

## Results

```{r 2-acoustic-similarity-mod, echo=1}
similarity_mod <- lmer(
  similarity_z ~ edge_generation_n + (edge_generation_n|name) + (edge_generation_n|category),
  data = acoustic_similarity_judgments
)

similarity_preds <- data_frame(edge_generation_n = 1:7) %>%
  cbind(., predictSE(similarity_mod, newdata = ., se = TRUE)) %>%
  rename(similarity_z = fit, se = se.fit) %>%
  recode_edge_generations
```

```{r, results="asis"}
broom::tidy(similarity_mod, effects="fixed") %>%
  knitr::kable(digits = 2)
```

```{r 2-similarity-judgments-plot}
similarity_judgments_means <- acoustic_similarity_judgments %>%
  group_by(edge_generations, category) %>%
  summarize(similarity_z = mean(similarity_z, na.rm = TRUE)) %>%
  recode_edge_generations

set.seed(949)
gg_similarity_judgments <- ggplot(similarity_judgments_means) +
  aes(x = edge_generations, y = similarity_z) +
  geom_point(aes(color = category), position = position_jitter(0.6, 0.0),
             size = 2, alpha = 0.8) +
  geom_smooth(aes(group = 1, ymin = similarity_z - se, ymax = similarity_z + se),
              data = similarity_preds, stat = "identity",
              alpha = 0.2, color = "gray") +
  scale_x_discrete("Generation") +
  scale_y_continuous("Acoustic similarity") +
  scale_color_brewer("Category", palette = "Set2") +
  global_theme +
  theme(legend.position = "top")
gg_similarity_judgments
```

## Discussion